Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-09-09 vesicle_code/docs/permeableVes/main.tex
added shear figure

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Shear Flow}
We consider a semi-permeable vesicle in the shear flow
$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability
rates $\beta$ and shear rates $\dot{\gamma}$. Depending on its reduced
area and viscosity contrast, two-dimensional vesicles either tank tread
or tumble~\cite{fin-lam-sei-gom2008,kra-win-sei-lip1996}. Since we are
considering semi-permeable vesicles, we assume there is no viscosity
contrast, and tumbling is not possible.

We initialize an elliptical vesicle with reduced area $\nu = 0.65$, and
with its long axis oriented in the $y$-direction. For all permeability
rates and shear rates, the semi-permeable vesicle tilts to an
inclination angle and undergoes tank treading dynamics. Because of the
semi-permeability, the initial and final reduced areas differ. In
Figure~\ref{fig:shearPhaseDiagram}, we plot the final shape of the
vesicle for various permeability rates, $\beta$, and shear rates
$\dot{\gamma}$. The shear rate has the largest effect on the final
reduced area.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Shear Flow}
We consider a semi-permeable vesicle in the shear flow
$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability
rates $\beta$ and shear rates $\dot{\gamma}$. Depending on its reduced
area and viscosity contrast, two-dimensional vesicles either tank tread
or tumble~\cite{fin-lam-sei-gom2008,kra-win-sei-lip1996}. Since we are
considering semi-permeable vesicles, we assume there is no viscosity
contrast, and tumbling is not possible.
\begin{figure}[htp]
  \centering
  \input{figures/shearSS.tikz}
  \caption{\label{fig:shearSS} The reduced area of a semi-permeable
  vesicle in a shear flow. The final reduced area is nearly independent
  of the initial reduced area.}
\end{figure}

In the quiescent flow, the steady state vesicle shape is independent of
the initial vesicle shape. Here we test if a similar results holds with
an imposed flow. In Figure~\ref{fig:shearSS}, we plot the reduced area
of four vesicles with different initial reduced areas. The final shape
depends on the initial vesicle length, but not on its initial reduced
area. Therefore, for this example we only consider vesicles with the
initial reduced area $\nu = 0.65$. For all permeability rates and shear
rates, the semi-permeable vesicle tilts to an inclination angle and
undergoes tank treading dynamics. Because of the semi-permeability, the
initial and final reduced areas differ. In
Figure~\ref{fig:shearPhaseDiagram}, we plot the final shape of the
vesicle for various permeability rates, $\beta$, and shear rates
$\dot{\gamma}$. The shear rate has the largest effect on the final
reduced area.
